---
title: "PDF reports"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{PDF reports}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
# Skip the slow rendering chunks on CRAN's auto-check farm. Locally,
# on CI, and under devtools::check(), `NOT_CRAN` is set and the chunks
# build their figures. Keeps the vignette buildtime well under the
# 10-minute CRAN budget (see r/cran-comments.md, v2.0.4 history).
NOT_CRAN <- identical(tolower(Sys.getenv("NOT_CRAN")), "true")
```

# PDF reports

`to_pdf_report()` produces a multi-page US-Letter-landscape PDF combining
the venn diagram, UpSet plot, statistics tables, network view, and a
methodology page — equivalent to the web tool's "Generate Report" button.

```{r load}
library(vennDiagramLab)
result <- analyze(load_sample("dataset_real_cancer_drivers_4"))
```

## Generating the report

Save to a temporary file (vignettes shouldn't write into the package
directory):

```{r generate, eval = NOT_CRAN && (getRversion() >= "4.6")}
out <- tempfile(fileext = ".pdf")
to_pdf_report(result, path = out, title = "Cancer driver overlap")
file.exists(out)
file.size(out)   # bytes
```

(The chunk above is gated on `R >= 4.6` because the report embeds an UpSet
panel via `ComplexUpset`, whose CRAN release (1.3.3) is incompatible with
`ggplot2 >= 4.0` on older R. See `?vennDiagramLab::to_pdf_report` for
context and workarounds.)

## What the report contains

By default, every report has 5 page types:

1. **Overview** — metadata (timestamp, dataset, set count) + set-size table.
2. **Venn + UpSet** — rasterized venn (left) + UpSet plot (right).
3. **Statistics** — Jaccard / Dice / Hypergeometric tables (per-page on 7+
   sets).
4. **Network** — set-relationship graph + significant edges list.
5. **About** — methodology notes (Venn / UpSet / Network / metric
   definitions).

Pages 4 (network) and 5 (about) can be turned off:

```{r minimal, eval = FALSE}
to_pdf_report(result, "venn_only.pdf",
              include_network = FALSE,
              include_about   = FALSE)
```

## What's next

* `vignette("v02_real_cancer_drivers")` — see the analysis that feeds the
  report.
* `vignette("v08_custom_styling_and_export")` — multi-format export
  beyond PDF (SVG, PNG).
